Optimal (Multiway) Spatial Joins

### 2024-05-19 msj.tex
yufei

In terms of techniques, our primary contribution is a result on the mathematical structure of the $k$-SJ problem. Specifically, for any $n \ge 1$ and $k \ge 2$, define function $F(n, k)$ to be the lowest value such that any instance of the $k$-SJ problem with input size $n$ and output size $\out$ can be solved in $F(n, k) + O(\out)$ time. Specificaly, define $F(n, 1) = n$ for any $n \ge 1$. Our main technical contribution can now be stated as:

\begin{theorem} \label{thm:main}
    d
\end{theorem}

>>>>

In terms of techniques, our primary contribution is a result on the mathematical structure of $k$-SJ. Specifically, for any $n \ge 1$ and $k \ge 2$, define function $F(n, k)$ to return the lowest positive integer such that our $k$-SJ algorithm can solve any instance of the $k$-SJ problem with input size $n$ and output size $\out$ in $F(n, k) + O(\out)$ time. Our main technical contribution can now be stated as:

\begin{theorem} \label{thm:main}
    For any $n \ge 1$ and $k \ge 3$, it holds that 
    \myeqn{
        F(n, k) = O(k^3) \cdot ( F(n, k-1) + n \log n).
        \label{eqn:main:reccurrence}
    }
\end{theorem}
